---
title: "Analysis_survey_responses"
author: "Josep Espasa Reig"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r}

rm(list = ls())

library(sjlabelled)
library(haven)
library(fs)
library(here)
library(magrittr)
library(tidyverse)

```

# Read all surveys

Everything was found here: https://ajuntament.barcelona.cat/en/content/public-opinion-poll-register-0

RDS
```{r}

path_all_surveys <- fs::dir_ls(here("data", "survey", "omnibus_surveys"))

#all_surveys_data <- map(path_all_surveys, read_rds)


```

SPSS
```{r}

path_all_sav_files <- dir_ls(here("data", "survey", "omnibus_surveys", "sav"))

  # we are interested in the labels to see which variables had something to do with bicicles

all_surveys_spss_data <- map(path_all_sav_files, read_sav)

names(all_surveys_spss_data) <- names(all_surveys_spss_data) %>%
  str_remove("C:/Users/josep/Desktop/R/barcelona_bike/data/survey/omnibus_surveys/sav/")

```



# Check which surveys contain vars related to biking

```{r}

labels_all_surveys <- map(all_surveys_spss_data, sjlabelled::get_label)

lookup_names_labels <- map(all_surveys_spss_data, function(x){
  
  data_frame(var_names = names(x), 
             var_labels = sjlabelled::get_label(x))
  
})

labels_all_surveys %>%
    map(~ .x %>% str_subset("BICI"))

```

# Main socio-demographic questions

## Age

Careful, some surveys have people with less than 16 yo, others they don't.

We will assume that all responses come from the same population. It's not ideal, but looks like the only feasible option.
```{r}

age_vars_name <- lookup_names_labels %>%
  map(~ .x$var_labels %>% str_which(pattern = "EDAT"))

age_vars_name %<>%
  map_dbl(min)

age_all_surveys <- all_surveys_spss_data %>%
  map2(.y = age_vars_name, ~ .x %>% 
         select(.y) )

age_all_surveys_categorical <- age_all_surveys %>%
  map(~ .x %>% mutate_all(function(x){cut(x, breaks = c(0, 16, 25, 40, 65, 80, 100))}))

# Recode age variable into categories

```



## District

```{r}

district_vars_name <- lookup_names_labels %>%
  map(~ .x$var_labels %>% str_which(pattern = "DISTRICTE"))

district_all_surveys <- all_surveys_spss_data %>%
  map2(.y = district_vars_name, ~ .x %>% select(.y) )

district_lookup_names <- data_frame(district_name = district_all_surveys$r16038_Òmnibus_Desembre_A_BDD_V_1_0.sav %>% get_labels() %>% .[[1]], district = 1:10)

```

Perform a check of proportion of district

Cool, district was used as quotas! 
Also, samples by district are rather small.
```{r eval=FALSE, include=FALSE}

district_all_surveys %>%
  map(~ .x %>% as_vector) %>%
  map(table)

```


# Main questions of interest 

Q1 Uses bike to move around BCN - utilitza bicicleta per desplacar-se per BCN
Q2 Uses bicing - en bicing
Q3 How do you rate the bike lanes in BCN - Com valora la xarxa de carrils bici a la ciutat de Barcelona


# Main bike questions

## Q1 - UTILITZA BICICLETA PER DESPLAÇAR-SE PER BARCELONA
```{r}

q1_exists <- lookup_names_labels %>%
  map_lgl(~ any(str_detect(.x$var_labels, "UTILITZA BICICLETA PER DESPLAÇAR-SE PER BARCELONA")))

q1_index <- lookup_names_labels %>%
  map(~ which(.x$var_labels == "UTILITZA BICICLETA PER DESPLAÇAR-SE PER BARCELONA") ) %>%
  unlist

q1_all_surveys <- all_surveys_spss_data[q1_exists] %>%
  map2(.y = q1_index, ~.x[,.y])

```

Awesome, different labels in same question!
```{r}

map(q1_all_surveys, ~get_labels(.x)) 

```

```{r}
  # multiple categories for bike users
index_multiple_categories <- map_dbl(q1_all_surveys, ~get_labels(.x)[[1]] %>% length) != 3

q1_all_surveys_recoded <- q1_all_surveys

      # recode for vars with only yes/no
q1_all_surveys_recoded[!index_multiple_categories] <- q1_all_surveys[!index_multiple_categories] %>%
  map(~.x %>% as_vector == 1)
      # recode for vars with multiple user categories
q1_all_surveys_recoded[index_multiple_categories] <- q1_all_surveys[index_multiple_categories] %>%
  map(~.x %>% as_vector < 4)

rm(index_multiple_categories)

```

```{r}
q1_all_surveys_recoded %>%
  map(sum)
```

## Df of Q1 with all other variables

```{r}
      # I'm sure this can be done in one step using pmap
q1_all_surveys_recoded_dfs <- map2(.x = q1_all_surveys_recoded,
     .y = district_all_surveys[q1_exists],
     ~ bind_cols(uses_bike = .x, .y))

q1_all_surveys_recoded_dfs %<>% map2(
     .y = age_all_surveys_categorical[q1_exists],
     ~ bind_cols(uses_bike = .x, .y))

for(i in seq_along(q1_all_surveys_recoded_dfs)){
  
  names(q1_all_surveys_recoded_dfs[[i]]) <- c("uses_bike", "district", "age_recoded")
  
}

```

## Q1 by district
Samples are rather small (<50)
```{r}

 q1_all_surveys_recoded_merged_df <- q1_all_surveys_recoded_dfs %>%
  bind_rows()

table_q1_by_district <- q1_all_surveys_recoded_merged_df %>%
  count(district, uses_bike) %>%
        group_by(district) %>%
        mutate(prop = n/sum(n)) %>%
        filter(uses_bike == T)

table_q1_by_district %<>%
  left_join(district_lookup_names)

table_q1_by_district %>%
  write_csv(here("interim_outputs", "survey_table_bike_use_district.csv"))

table_q1_by_district

```

## Q1 by age categories

```{r}

table_q1_by_age <- q1_all_surveys_recoded_merged_df %>%
  count(age_recoded, uses_bike) %>%
        group_by(age_recoded) %>%
        mutate(prop = n/sum(n)) %>%
        filter(uses_bike == T)

table_q1_by_age %>%
  write_csv(here("interim_outputs", "survey_table_bike_use_age.csv"))

table_q1_by_age

```

# Q1 by district and age categories 

```{r}

table_q1_by_district_and_age <- q1_all_surveys_recoded_merged_df %>%
  count(district, age_recoded, uses_bike) %>%
        group_by(district, age_recoded) %>%
        mutate(prop = n/sum(n)) %>%
        filter(uses_bike == T) %>%
    arrange(age_recoded, district)

table_q1_by_district_and_age %<>%
  left_join(district_lookup_names)

table_q1_by_district_and_age %>%
  write_csv(here("interim_outputs", "survey_table_bike_use_district_and_age.csv"))
            
table_q1_by_district_and_age

```

